---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  fig.dim = c(4, 4),
  dpi = 300
)
```

# StochasticArt

<!-- badges: start -->
<!-- badges: end -->

The goal of StochasticArt is, naturally, to generate stochastic art! This package is really just a fun personal project, but perhaps it will find its way to some curious explorers who have not thought about ways in which R can be used to create visually interesting things.

## Installation

You can install the development version of StochasticArt from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("christopher-rowe/StochasticArt")
```

## Examples

First, load the package.

```{r load}
library(StochasticArt)
```

Now try out some of the functions! If you don't specify a value to the `seed` argument, a random `seed` will be generated and printed to the console so that you can always regenerate a previous image.

Not specifying any arguments will always generate a random image, but I encourage you to mess around with some of the arguments to see how the output changes. And even better, check out the code underlying each of the functions!

```{r example1}
generate_fabric()
```

```{r example2}
generate_lines_and_polygons()
```

```{r example3}
generate_perception_matrix()
```

```{r example4}
generate_lines_and_rectangles()
```

```{r example5}
generate_panels()
```

```{r example6}
generate_circles()
```

```{r example7}
generate_string_waves()
```

